---
title: "Homework 5"
author: Maya Bunyan
output: github_document
---

This my solution to Homework 5!

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


# Problem 1

Read in the data

```{r}
homicide_df = 
  read_csv("./homicide_data/homicide-data.csv") %>%
  mutate (
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
  ) %>%
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Look more at the data.

```{r}
aggregate_df = 
  homicide_df %>%
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Prop test for a single city.

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>%  pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>%  pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>%
  unnest(tidy_tests) %>%
  select(city_state, estimate, conf.low, conf.high)
```


```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

# Problem 2

Import and tidy the data

```{r}
path_df = 
  tibble(
    path = list.files("lda_data")
  ) %>% 
  mutate(
    path_name = str_c("lda_data/", path),
    data = map(.x = path_name, ~read_csv(.x))
  ) %>%
  unnest(data) %>%
  select(-path_name) %>%
  separate(
    col = path,
    into = c("treatment_arm", "subject_id", "csv"),
    convert = T
  ) %>%
  select(-csv) %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "obs"
  ) %>% 
    mutate(
    treatment_arm = recode(treatment_arm, con = "control", exp = "experimental"),
    week = as.numeric(week)
  ) 
```

Create spaghetti plot showing observations on each subject over time

```{r}
path_df %>% 
  ggplot(aes(x = week, y = obs, group = subject_id, color = subject_id)) +
  geom_point() +
  geom_line() +
  facet_grid(. ~ treatment_arm)
```

From the graph, we see that overall, the observations appear to be relatively constant over time. However, for the experimental arm, the observations appear to be increasing over time. 

# Problem 3